---
title: 'Session 2: Raw Reads'
author: "Your Name"
date: "16 July 2016"
output: html_document
---

******
******
******
### Exercise

Import the example `fastq` file using the `ShortRead` package.

- How many reads are found?
- How long is each sequenced read?


```{r}
library(ShortRead)
fq <- readFastq("sample.fq1")
fq
```

******
******
******

```{r}
sread(fq)
myreads <- sread(fq)
```



******
******
******

### Exercise
- Use `subseq` to print the first five basees of the sequenced reads

```{r}
firstBases <- subseq(myreads,1,5)
firstBases
```


- How many reads start with five A's?
    + HINT: we can test for equality using `==` which gives a logical (`TRUE` or `FALSE`)
    + HINT: `table` can be used to get counts of how many different values occur in a vector
- What is the most-common five bases at the start of the reads
    + HINT: `sort` will produce a sorted version of a vector

******
******
******


```{r}

```

## Base counts with letterFrequency

```{r}
af <- letterFrequency(sread(fq), letters=c("A","C","G","T","N"))
head(af)
aS <- af[,1]
hist(aS)
```


******
******
******
### Exercise

- Create a vector to represent the "GC" content of each read
- What is the mean number of GC bases?
- Visualise the GC distribution using a histogram
- What reads have more than 60 GC bases?


******
******
******

```{r}


``` 


```{r}
plot(abc[1,],type="n",ylim=c(0,2000000))
text(abc[1,1:68],label="A",col="red")
text(abc[2,1:68],label="C",col="orange")
text(abc[3,1:68],label="G",col="blue")
text(abc[4,1:68],label="T",col="green")
```


## Dealing with qualities

```{r}
quality(fq)
myquals <- quality(fq)
encoding(quality(fq))
qm <- as(quality(fq), "matrix")
head(qm)

qualmeans <- colMeans(qm)
plot(qualmeans)
