---
title: "R recap"
author: "Your Name Here"
date: '15th February'
output: html_document
---


## Getting started

First load the wakefield package

```{r}
library(wakefield)
```

Now run this function

```{r}
random_patients <- function(n) {
  as.data.frame(r_data_frame(
    n,
    id,
    name,
    race,
    sex,
    smokes,
    height,
    birth(random = TRUE, x = NULL, start = Sys.Date() - 365 * 45, k = 365*2,by = "1 days"),
    state,
    pet,
    grade_level(x=1:3),
    died,    
    normal(name="Count"),
    date_stamp)
  )
}

```



```{r}
patients <- random_patients(100)
```

******
******
******

### Exercise

- What are the dimensions of the data frame?

- What columns are available?
  + HINT: see the `dim`, `ncol`, `nrow` and `colnames` functions
 
******
******
******


```{r }
```

******
******
******

### Exercise
- Can you think of two ways to access the Names of the patients?
- What type of object is returned?

******
******
******


```{r}
```



## Subsetting


******
******
******

### Exercise
- Make sure you can understand the behaviour of the following commands

******
******
******

```{r}
patients[1,2]
patients[2,1]
patients[c(1,2,3),1]
patients[c(1,2,3),c(1,2,3)]
```

******
******
******

### Exercise
- Make sure you can understand the behaviour of the following commands

******
******
******

```{r}
patients[1,]
patients[,1]
patients[,c(1,2)]
```



******
******
******

### Exercise

- How can we view all information about the first six patients?
   + HINT `head` is commonly-used to give a snapshot of a data frame.
Otherwise, you can use the `[row,column]` notation.

******
******
******

```{r}
```


******
******
******

### Exercise

- Can you create a data frame of dog owners?

******
******
******


```{r}

```


******
******
******

### Exercise

- Can you create a data frame of deceased patients with a 'count' < 0

```{r echo=FALSE}
patients[patients$Count <0 & patients$Died,]
```


******
******
******

```{r}

```


## Simple plotting



```{r}
hist(patients$Height)
```


```{r}
plot(patients$Height,patients$Count)
```


```{r}
barplot(table(patients$Race))
```

```{r}
barplot(table(patients$Pet))
```


```{r}
boxplot(patients$Count ~ patients$Died)
```


```{r}
plot(patients$Height,patients$Count,pch=16,
     col="red",xlab="Height",
     ylab="Count")
```


```{r}
boxplot(patients$Count ~ patients$Died,col=c("red","yellow"))
```

```{r}
png("myLittlePlot.png")
barplot(table(patients$Pet))
dev.off()
```
